Misexpression of germline programs with loss of the X-linked intellectual disability factor KDM5C

### 2024-05-20 submission/manuscript.Rmd
add commas to large numbers

bibliography: references.bib
csl: cell-reports.csl
indent: true
editor_options:
  chunk_output_type: console
---
```{r, knitrcommas, results='hide', echo = FALSE, warning=FALSE,message=FALSE,error=FALSE}
library(huxtable)

>>>>

bibliography: references.bib
csl: cell-reports.csl
indent: true
editor_options:
  chunk_output_type: console
---
```{r, knitrcommas, results='hide', echo = FALSE, warning=FALSE,message=FALSE,error=FALSE}
#adds commas to large numbers
library(huxtable)
